---
title: "Cabbages"
author: "Dorothy Decker!"
date: "Summer 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
# Assuming the data frame is called "veggy" and the required package is installed

library(ggplot2)

# Create a box plot
ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  xlab("Cult") +
  ylab("Vitamin C") +
  ggtitle("Box Plot of Vitamin C by Cult") +
  theme(plot.title = element_text(hjust = 0.5, size = 16))

```

If you look at the two boxes on the box plot, the two boxes are on different areas on the graph. They have nothing in common. When two boxes are that far apart, that means they are statistically different. They are completely displaced from each other. We may find a statistical difference between these two methods.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

With these numerical results, the average in c39 is 51.5, while the average in c52 is 64.4 which shows how different they are. The Q1 of the c52 box is bigger than the Q1 of the c39 box. The two places are disjoint from each other. By comparing the numerical results, we can further understand there may be a difference between the two.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```


According to the t test, the probability of getting a result that we just obtained is .00000003405. This number shows that there is a big difference between these two groups. We reject the hypothesis that says there is no difference. The alternative hypothesis is that the true difference in means between group c39 and group52 is not equal to 0. The two methods are different, there is a big difference.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the George Town videos collection.!-->

Today we used graphical, numerical, and inferential results to come to our conclusions. Each set of results further prove that there is a big difference between the VitC cultivation methods. Looking at the graphical results, for example, simply by looking at the picture, you can see they aren't the same. If they were the same, they would have similar graphs, but this isn't the case. They have totally different graphs. Looking at the other results, we can conclude they are statistically different. 
